The effect of linking assumptions and number of response options on inferred scalar implicature rate

### 2018-04-29 writeup.Rmd
added to intro

Because the basic reconstruction of the inference is much more easily characterized for  scalar implicatures than for other implicatures, scalar implicatures have served as a test bed for many questions in experimental pragmatics, including, but not limited to:
1. Are scalar inferences default inferences, in the sense that they arise unless blocked by (marked) contexts [@horn1984; @levinson2000; @Degen2015]?
2. Are scalar inferences default inferences, in the sense that they are computed automatically in online processing and only cancelled by context in a second effortful step if required by context) [@bott2004;@Breheny2006;@DegenTanenhaus2016;@Grodner2010;@huang2009]?
3. What are the (linguistic and extra-linguistic) factors that affect whether a scalar implicature is derived [@zondervan2010;@DegenTanenhaus2015; @DegenTanenhaus2016; @Degen2015; @DegenGoodman2014; @Bergen2012; @Breheny2006; @Breheny2013;@DeMarneffeTonhauser;@DeNeys2007;@Bonnefon2009]?
4. At what age do children acquire the ability to compute implicatures [@Noveck2001; @Papafragou2004; @Barner2011; Frank; @Musolino2004]? 
5. How much diversity is there across implicature types, and within scalar implicatures across scale types, in whether or not an implicature is computed [@Doran2012;@VanTiel2014]?

CONTINUE HERE: motivation for examining implicature rate assumptions:

* surging interest in differences in implicature rates (eg van tiel, dgen tanenhaus)
* implicature rates serve as basis for claims about online processing (bott & noveck, degen tanenhaus)
* implicature rates serve as basis for claims about children (bishop katsos, barner, frank)

* add @deneys2007
* @demarneffetonhauser for investigations of scalar adjectives, and @vantiel

>>>>

Because the basic reconstruction of the inference is much more easily characterized for  scalar implicatures than for other implicatures, scalar implicatures have served as a test bed for many questions in experimental pragmatics, including, but not limited to:

1. Are scalar inferences default inferences, in the sense that they arise unless blocked by (marked) contexts [@horn1984; @levinson2000; @Degen2015]?

2. Are scalar inferences default inferences, in the sense that they are computed automatically in online processing and only cancelled by context in a second effortful step if required by context) [@bott2004;@Breheny2006;@DegenTanenhaus2016;@Grodner2010;@huang2009;@Politzer-Ahles2013;Tomlinson2013]?

3. What are the (linguistic and extra-linguistic) factors that affect whether a scalar implicature is derived [@Zondervan2010;@DegenTanenhaus2015; @DegenTanenhaus2016; @Degen2015; @DegenGoodman2014; @Bergen2012; @Breheny2006; @Breheny2013;@DeMarneffeTonhauser;@DeNeys2007;@Bonnefon2009;Chemla2011;Potts2015]?

4. How much diversity is there across implicature types, and within scalar implicatures across scale types, in whether or not an implicature is computed [@Doran2012;@VanTiel2014]?

5. At what age do children acquire the ability to compute implicatures [@Noveck2001; @Papafragou2004; @Barner2011; Frank; @Musolino2004;@Katsos2011]?

In addressing all of these questions, it has been crucial to obtain estimates of **implicature rates**. For 1., implicature rates from experimental tasks can be taken to inform whether scalar implicatures should be considered default inferences. For 2., processing measures on responses that indicate implicatures can be compared to processing measures on responses that indicate literal interpretations. For 3., contextual effects can be examined by comparing implicature rates across contexts. For 4., implicature rates can be compared across scales (or across implicature types). For 5., implicature rates can be compared across age groups.

A standard measure that has stood proxy for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;Degen2014]. In these kinds of tasks, participants are provided a set of facts, either presented visually or via their own knowledge of the world. They are then asked to judge whether a sentence intended to describe those facts is true or false (or alternatively, whether it is right or wrong, or they are asked whether they agree or disagree with the sentence). The crucial condition for assessing implicature rates in these kinds of studies typically consists of a case where the facts are such that the stronger alternative is true and the utterance is underinformative. For instance, @Bott2004 asked participants to judge sentences like 'Some elephants are mammals', when world knowledge dictates that all elephants are mammals. Similarly, @DegenTanenhaus2015 asked participants to judge sentences like 'You got some of the gumballs' in situations where the visual evidence indicated that the participant received all the gumballs from a gumball machine. In these kinds of scenarios, the story goes, if a participant responds 'FALSE', that indicates that they computed a scalar implicature, eg to the effect of 'Not all elephants are mammals' or 'You didn't get all of the gumballs'. If instead a participant responds 'TRUE', that is taken to indicate that they interpreted the utterance literally as `Some, and possibly all, elephants are mammals' or 'You god some, and possibly all, of the gumballs'.

People who have discussed issues with the TVJP:
@BenzGotzner; @Geurts2009; @Geurts2010; @Katsos2011

* @demarneffetonhauser for investigations of scalar adjectives,
